\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[margin,line]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{fourier-orns}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}
\usepackage[style=iso]{datetime2}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=8.9in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Ryan A.~Divan --- Curriculum Vitae (as of \today)}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

% Give hyperref some metadata
\hypersetup{pdftitle={Ryan A. Divan — Curriculum Vitae (CV)},
  pdfauthor={Ryan A. Divan},
  pdfsubject={Ryan A. Divan's academic curriculum vitae (CV)},
  pdfkeywords={mathematics, machine learning, numerical analysis, numerical linear algebra, randomized methods, computational mathematics}}

% I want small caps for the section style
\def\sectionfont{\sc}

% Generate a PDF TOC
\let\oldsection\section
\def\section#1{\oldsection{#1}%
\phantomsection%
\addcontentsline{toc}{section}{#1}%
}

% The above seems to screw up the spacing for sections that start with lists...
\newcommand{\secstartswithlist}{\leavevmode \vspace{-\baselineskip}}

\begin{document}

\newcommand{\myname}{Ryan A.~Divan}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \myname \vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

\input{ContactContent.tex}

% \section{Citizenship}
% United States
\vspace{-1.0em}
\section{Education}

{\bf B.A., Mathematics,} Princeton University, Princeton, NJ \hfill {\bf May 2028 (expected)}\\
\vspace*{-.1in}
\begin{itemize}
\item[ ] G.P.A.: 3.87/4.00
\item[ ] \emph{Relevant coursework:} Numerical Analysis / Scientific Computing, Probabilistic Combinatorics, Probability Theory, Linear Algebra, Theoretical Machine Learning, Algebra I, Real Analysis
\end{itemize}
\section{Research Positions}
{\bf Student Researcher,} Princeton University PACM, NJ
\hfill {\bf October 2025--Present}
\begin{itemize}
\item[ ] Conduct independent research in randomized numerical linear algebra under Prof. Marc Gilles.
\end{itemize}
{\bf Summer Research Scholar,} NJGSS @ Drew University, Madison, NJ \hfill {\bf  July-August 2023}
\begin{itemize}
\item[ ] Selected as one of 60 students statewide to conduct fully-funded summer research.
\end{itemize}

% Added to improve page breaks

\section{Research Experience}
1. {\it Randomly pivoted Cholesky: investigation and applications}
\begin{itemize}
    \item[] Advised by Prof. Marc Gilles, investigated theory and implemented machine learning applications of the RPCholesky algorithm (Chen–Epperly–Tropp–Webber, 2025) in Python/NumPy.
\end{itemize}
2. {\it Effect of Fiberware / PLA Compostables on Compost Maturity}, with Daniela Cruz.
\begin{itemize}
    \item[] Advised by Prof. Xinning Zhang, analyzed effect of fiberware composition on compost maturity by proxy of emissions with R. Presented at Princeton Geoscience Department poster session.
\end{itemize}
3. {\it Combating Malaria: Drug Discovery Approach Using Thiazole Derivatives Against PfPKG Enzymes}
\begin{itemize}
    \item[] Advised by Prof. Fina Liotta, conducted organic synthesis and in silico analysis using UCSF Chimera for docking simulations. Presented at the David Miyamoto Scholars Conference.
\end{itemize}

\section{Industry Experience}
{\bf Founder \& COO,} EVAL Gaming Inc., Princeton, NJ
\hfill {\bf August 2024--Present}
\begin{itemize}
\item[ ] Lead data analysis and modeling efforts for player performance datasets in scholastic esports.
\end{itemize}
{\bf Data Analyst Intern,} Mendocino Food Consulting, Remote \hfill {\bf July-September 2025}
\begin{itemize}
\item[ ] Created various data science and web development efforts for the consultancy.
\end{itemize}
{\bf Summer Accelerator Fellow,} Keller Center, Princeton, NJ \hfill {\bf  June-August 2025}
\begin{itemize}
\item[ ] Awarded \$30,000 in funding to manage team and build data analytics company, EVAL Gaming.
\end{itemize}

{\bf Data Analyst Extern,} Mobalytics, Remote \hfill {\bf  May-June 2024}
\begin{itemize}
\item[ ] Performed data analysis and market research for expansion into new esports markets.
\end{itemize}

\section{Honors and Awards}
{\bf Venture Award Grantee,}
Princeton Student Ventures,
\hfill {\bf 2025}\\
\\
{\bf ESAF Scholar,}
Entertainment Software Association Foundation,
\hfill {\bf 2025}\\
\\
{\bf U.S. Presidential Scholar Semifinalist,} U.S. Department of Education \hfill {\bf 2024}\\
\\
{\bf National Merit Scholarship Finalist,} National Merit Foundation \hfill {\bf 2024}\\
\\
{\bf NJ Governor's School in the Sciences Scholar,} NJ Department of Education \hfill {\bf 2023}\\

% Added to improve page breaks
\vspace{-1em}

\section{Teaching Experience}
{\bf Undergraduate Course Assistant}, Princeton University
\vspace*{.05in}
\begin{itemize}
\item[ ] MAT215, Single Variable Analysis with an Introduction to Proofs \hfill {\bf Fall 2025}
\item[ ] MAT217, Honors Linear Algebra \hfill {\bf Spring 2026}
\end{itemize}
%\newpage{}

\section{Presentations, Research Talks, and Assorted Outreach}

{\bf Research Presentations}
\vspace*{.05in}
\begin{itemize}

\item[] Princeton Geosciences Department Poster Session
  \hfill {\bf December 2024} \\
    \hspace*{1em} Poster: {\it Effect of Fiberware / PLA on Compost Maturity}
\item[] David Miyamoto Scholars Conference @ Drew University
  \hfill {\bf August 2023} \\
  \hspace*{1em} Paper: {\it Combating Malaria: A Drug Discovery Approach}

\end{itemize}


{\bf Outreach}
\vspace*{.05in}
\begin{itemize}

\item[] Invited speaker, Games for Change Next-Gen Summit
\hfill {\bf February 17, 2025} \\
 \hspace*{1em} Panel: Creator Panel with EVAL Gaming

\item[] Keller Center eLab Demo Day 2025
  \hfill {\bf July 31, 2025} \\
  \hspace*{1em} Pitch: ``EVAL Gaming: Connecting Gamers to College Scholarships''

\item[] Guest on {\it The Video Gamers Podcast} \\
\hspace*{1em}  Episode: 
\href{https://open.spotify.com/episode/4d3PQMIizg27Vtax5hSFn1?si=56d288270e9849c2}{Gaming Scholarships \& The Future of Esports in Schools}
\hfill
{\bf July 18, 2025}

\item[] Invited speaker, Garden State Esports Summit 2024
\hfill {\bf November 22, 2024} \\
 \hspace*{1em} Panel: Voices of Esports

\end{itemize}

\section{Computer Skills}
%{\bf Languages---}%
Proficient in Python and scientific computing / ML libraries (NumPy, Pandas, Tensorflow, PyTorch)
Experience in Java, C\#, Lean, Javascript.
Markup languages: \LaTeX, HTML, CSS, Markdown.

\section{Other Projects}

{\bf Kachi (skincare data app),}
exited,
\hfill {\bf 2025}
\begin{itemize}
    \item[] Next.js, Wordware, Python (FastAPI)
\end{itemize}
{\bf Project Leo (2D Unity platformer game),}
\href{https://lunarflame.dev/projects/project-leo/}{ lunarflame.dev/projects/project-leo},
\hfill {\bf 2023-2025}
\begin{itemize}
    \item[] Unity, C\#, Python
\end{itemize}
{\bf Assorted Rocket League articles, Dignitas,} \href{https://dignitas.gg/articles?author=xeno}{dignitas.gg}, \hfill {\bf 2022-2024}

% {\bf Operating systems---}%
% Mac OS, Linux/*nix.

% Twiddle this for spacing
% \newpage

% \ifx\nopubs\undefined
% \input{PubsContent.tex}
% \else
%
% \fi

%\input{TalksContent.tex}

% \newpage{}

\section{References}
\vspace*{.05in}
\parbox{\textwidth}{%
{\bf Prof. Marc Gilles,} Assistant Professor of Mathematics, Princeton University \\
212 Fine Hall \\
Princeton, NJ 08540 \\
email: \href{mailto:gilles@princeton.edu}{gilles@princeton.edu} \\
office phone: \href{tel:1-609-258-4200}{1-609-258-4200}}
\par
\parbox{\textwidth}{%
{\bf Dr. Bryan Quoc Le,} Founder \& CEO, Mendocino Food Consulting\\
10451 Nichols Lane \\
Mendocino, CA 95460 \\
email: \href{mailto:bryan@mendocinofoodconsulting.com}{bryan@mendocinofoodconsulting.com} \\
office phone: \href{tel:1-814-883-2069}{1-814-883-2069}}
\par

\parbox{\textwidth}{%
{\bf Prof. Derek Lidow,} Professor of the Practice in the Keller Center, Princeton University\\
34 Chambers Street \\
Princeton, NJ 08540 \\
email: \href{mailto:dlidow@princeton.edu}{dlidow@princeton.edu} \\
office phone: \href{tel:1-609-258-4756}{1-609-258-4756}}
\par

\end{resume}
\end{document}

% Local Variables:
% mode: latex
% End:
